Title: Week 2 – Course toolbox
Author: Dr. Glasbrenner
Author_Image: https://www.gravatar.com/avatar/49802fdfa5a0e63b3d932a5179d41c1e
Date: 2019-01-28 08:00
Tags: class notes
Slug: week02-materials
Show_summary: false
Show_link: false

```{r setup, include = FALSE}
icon_pdf <- '<i class="fas fa-file-pdf" data-fa-transform="grow-16"></i>&nbsp;'
icon_pen <- '<i class="fa fa-pen-square" data-fa-transform="grow-16"></i>&nbsp;'
icon_book <- '<i class="fa fa-book" data-fa-transform="grow-16"></i>&nbsp;'
icon_github <- '<i class="fab fa-github-alt" data-fa-transform="grow-8"></i>&nbsp;'
icon_pencil <- '<i class="fas fa-pencil-alt" data-fa-transform="grow-16"></i>&nbsp;'
icon_laptop <- '<i class="fa fa-laptop" data-fa-transform="grow-16"></i>&nbsp;'
```

[Readings]{.h2}

::: {.no-bullets}
*   [`r icon_book` &nbsp; [Reading 2]{.card-downloads-format}][reading02] (Complete by: Feb-04)
:::

<div style="margin-bottom: 1em"></div>

[Homeworks]{.h3}

::: {.no-bullets}
*   [`r icon_pen` &nbsp; [Mini-homework 2a -- R Markdown practice]{.card-downloads-format}][mini-homework02a] (Due: Feb-05 @ 11:59pm)

*   [`r icon_pen` &nbsp; [Mini-homework 2b -- Visualization practice]{.card-downloads-format}][mini-homework02b] (Due: Feb-05 @ 11:59pm)
:::

<div style="margin-bottom: 1em"></div>

[Videos]{.h3}

(Watch by: Feb-04)

**01 - Reproducible toolbox - Reproducibility in science**

```{r reproducible-toolbox-01-reproducibility-in-science, echo = FALSE}
vembedr::embed_youtube(id = "-Pw-z_rROlw", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

**02 - Reproducible toolbox - Reproducible research toolkit**

```{r reproducible-toolbox-02-reproducible-research-toolkit, echo = FALSE}
vembedr::embed_youtube(id = "GicSJT_VorM", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

[Slides]{.h3}

::: {.no-bullets}
*   [`r icon_pdf` &nbsp; [01 - Reproducibility in science]{.card-downloads-format}][slides-01]

*   [`r icon_pdf` &nbsp; [02 - Reproducible research toolkit]{.card-downloads-format}][slides-02]
:::

[slides-01]:        /doc/reproducible_toolbox_01_reproducibility_in_science.pdf
[slides-02]:        /doc/reproducible_toolbox_02_reproducible_research_toolkit.pdf
[reading02]:        /assignments/reading02/
[mini-homework02a]: /assignments/minihw02a-rmarkdown-practice/
[mini-homework02b]: /assignments/minihw02b-visualization-practice/
