Title: Week 9 – Inference and simulation
Author: Dr. Glasbrenner
Author_Image: https://www.gravatar.com/avatar/49802fdfa5a0e63b3d932a5179d41c1e
Date: 2019-04-01 08:00
Tags: class notes
Slug: week09-materials
Show_summary: false
Show_link: false

```{r setup, include = FALSE}
icon_pdf <- '<i class="fas fa-file-pdf" data-fa-transform="grow-16"></i>&nbsp;'
icon_pen <- '<i class="fa fa-pen-square" data-fa-transform="grow-16"></i>&nbsp;'
icon_book <- '<i class="fa fa-book" data-fa-transform="grow-16"></i>&nbsp;'
icon_github <- '<i class="fab fa-github-alt" data-fa-transform="grow-8"></i>&nbsp;'
icon_pencil <- '<i class="fas fa-pencil-alt" data-fa-transform="grow-16"></i>&nbsp;'
icon_laptop <- '<i class="fa fa-laptop" data-fa-transform="grow-16"></i>&nbsp;'
```

[Readings]{.h2}

::: {.no-bullets}
*   [`r icon_book` &nbsp; [Reading 9]{.card-downloads-format}][reading09] (Complete by: Apr-8 @ 11:59pm)
:::

<div style="margin-bottom: 1em"></div>

[Homeworks]{.h2}

::: {.no-bullets}
*   [`r icon_pen` &nbsp; [Mini-homework 7 -- Who busts the Mythbusters?]{.card-downloads-format}][mini-homework07] (Due: Apr-12 @ 11:59pm)
:::

<div style="margin-bottom: 1em"></div>

[Videos]{.h2}

(Watch by: Apr-8)

**Inference and simulation - 01 - Gender discrimination case study**

```{r inference-and-simulations-01-gender-discrimination-case-study, echo = FALSE}
vembedr::embed_youtube(id = "EL9bbzblRq8", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

**Inference and simulation - 02 - A hypothesis test as a court trial**

```{r inference-and-simulations-02-a-hypothesis-test-as-a-court-trial, echo = FALSE}
vembedr::embed_youtube(id = "LzsLhuxYiMs", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

**Inference and simulation - 03 - A manual simulation of the gender discrimination experiment**

```{r inference-and-simulations-03-a-manual-simulation-of-the-gender-discrimination-experiment, echo = FALSE}
vembedr::embed_youtube(id = "hjVjAzuMRDM", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

**Inference and simulation - 04 - Simulating the gender discrimination experiment in R**

```{r inference-and-simulations-04-simulating-the-gender-discrimination-experiment-in-r, echo = FALSE}
vembedr::embed_youtube(id = "8wQ-uU611vI", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

[Slides]{.h2}

::: {.no-bullets}
*   [`r icon_pdf` &nbsp; [01 - Gender discrimination case study]{.card-downloads-format}][slides-01]

*   [`r icon_pdf` &nbsp; [02 - A hypothesis test as a court trial]{.card-downloads-format}][slides-02]

*   [`r icon_pdf` &nbsp; [03 - A manual simulation of the gender discrimination experiment]{.card-downloads-format}][slides-03]

*   [`r icon_pdf` &nbsp; [04 - Simulating the gender discrimination experiment in R]{.card-downloads-format}][slides-04]
:::

[slides-01]:          /doc/inference_and_simulation_01_gender_discrimination_case_study.pdf
[slides-02]:          /doc/inference_and_simulation_02_a_hypothesis_test_as_a_court_trial.pdf
[slides-03]:          /doc/inference_and_simulation_03_a_manual_simulation_of_the_gender_discrimination_experiment.pdf
[slides-04]:          /doc/inference_and_simulation_04_simulating_the_gender_discrimination_experiment_in_r.pdf
[reading09]:          /assignments/reading09/
[mini-homework07]:    /assignments/minihw07-who-busts-the-mythbusters/
