Title: Week 3 – Data visualization
Author: Dr. Glasbrenner
Author_Image: https://www.gravatar.com/avatar/49802fdfa5a0e63b3d932a5179d41c1e
Date: 2019-02-04 08:00
Tags: class notes
Slug: week03-materials
Show_summary: false
Show_link: false

```{r setup, include = FALSE}
icon_pdf <- '<i class="fas fa-file-pdf" data-fa-transform="grow-16"></i>&nbsp;'
icon_pen <- '<i class="fa fa-pen-square" data-fa-transform="grow-16"></i>&nbsp;'
icon_book <- '<i class="fa fa-book" data-fa-transform="grow-16"></i>&nbsp;'
icon_github <- '<i class="fab fa-github-alt" data-fa-transform="grow-8"></i>&nbsp;'
icon_pencil <- '<i class="fas fa-pencil-alt" data-fa-transform="grow-16"></i>&nbsp;'
icon_laptop <- '<i class="fa fa-laptop" data-fa-transform="grow-16"></i>&nbsp;'
```

[Readings]{.h2}

::: {.no-bullets}
*   [`r icon_book` &nbsp; [Reading 3]{.card-downloads-format}][reading03] (Complete by: Feb-11)
:::

<div style="margin-bottom: 1em"></div>

[Homeworks]{.h2}

::: {.no-bullets}
*   [`r icon_pen` &nbsp; [Mini-homework 3 -- Visualization by example]{.card-downloads-format}][mini-homework03] (Due: Feb-12 @ 11:59pm)
:::

<div style="margin-bottom: 1em"></div>

[Videos]{.h2}

(Watch by: Feb-11)

**01 - Data visualization as communication**

```{r data-visualization-01-communication, echo = FALSE}
vembedr::embed_youtube(id = "W5Fnc4U3sS4", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

**02 - Examining numerical data**

```{r data-visualization-02-examining-numerical-data, echo = FALSE}
vembedr::embed_youtube(id = "Dtveq_kYlKQ", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

**03 - Describing visualizations**

```{r data-visualization-03-describing, echo = FALSE}
vembedr::embed_youtube(id = "HVFek-6iz-M", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

**04 - Data visualization with ggplot2**

```{r data-visualization-04-data-visualization-with-ggplot2, echo = FALSE}
vembedr::embed_youtube(id = "pmjM0mz_1Es", height = 350, allowfullscreen = TRUE, frameborder = 0)
```

[Slides]{.h2}

::: {.no-bullets}
*   [`r icon_pdf` &nbsp; [01 - Data visualization as communication]{.card-downloads-format}][slides-01]

*   [`r icon_pdf` &nbsp; [02 - Examining numerical data]{.card-downloads-format}][slides-02]

*   [`r icon_pdf` &nbsp; [03 - Describing visualizations]{.card-downloads-format}][slides-03]

*   [`r icon_pdf` &nbsp; [04 - Data visualization with ggplot2]{.card-downloads-format}][slides-04]
:::

[slides-01]:        /doc/data_visualization_01_data_visualization_as_communication.pdf
[slides-02]:        /doc/data_visualization_02_examining_numerical_data.pdf
[slides-03]:        /doc/data_visualization_03_describing_visualizations.pdf
[slides-04]:        /doc/data_visualization_04_data_visualization_with_ggplot2.pdf
[reading03]:        /assignments/reading03/
[mini-homework03]:  /assignments/minihw03-visualization-by-example/
